\subsection{Controlled simulation details}
\label{app:soft-fqi-simulation-details}

\paragraph{Environment and grid reference.}
The benchmark is a continuous two-dimensional navigation MDP with five
discrete actions, nonlinear stochastic dynamics, a high-reward goal basin, and
a lower-reward decoy basin. The decoy is used only to induce behavior policies
whose stationary distribution differs from the soft-optimal stationary
distribution. We compute reference quantities on a grid: soft value iteration
at $\tau=10^{-3}$ gives $Q^\star_\tau$, the soft-optimal policy, and the target
stationary state-action distribution. Oracle density ratios are the target
stationary probabilities divided by the corresponding behavior probabilities.

\paragraph{Behavior regimes.}
Only the data-collection distribution changes. The nearly on-policy regime
uses $0.999\pi^\star+0.001\pi_{\mathrm{unif}}$ and has TV distance $0.002$
from the target stationary distribution with oracle ESS fraction $0.999$. The
mild-shift regime uses
$0.55\pi^\star+0.35\pi_{\mathrm{decoy}}+0.10\pi_{\mathrm{unif}}$ (TV $0.507$,
ESS fraction $0.428$, 99th percentile ratio $1.5$). The severe-shift regime
uses $0.20\pi^\star+0.70\pi_{\mathrm{decoy}}+0.10\pi_{\mathrm{unif}}$ (TV
$0.964$, ESS fraction $0.017$, 99th percentile ratio $34$).

\paragraph{Estimated stationary weights.}
The estimated method uses the same state-action samples as FQI. The density
ratio and critic are represented in a shared finite RBF-polynomial dictionary,
and the ratio is fit by the DICE-style saddle-point moment equations with
ridge regularization. We target discounted stationary ratios with
$\gamma_w=0.95$, which regularizes the stationary-flow equations while keeping
the weights close to the oracle stationary correction.

\paragraph{Diagnostics.}
Stationary projected Bellman error is the Bellman residual after projection in
the target stationary norm. Advantage-centered stationary $Q$ error subtracts
the within-state action average before computing target-stationary error, so
it removes raw $Q$ shifts that do not affect low-temperature action choice.
Panel~D reports severe-shift win rates against unweighted FQI for the three
diagnostics shown or discussed in the main text.

\paragraph{Annealing sensitivity.}
The main experiment uses direct low-temperature fitting at $\tau=10^{-3}$. To
check whether continuation becomes more important near the hard-max limit, we
also repeat the experiment at $\tau=10^{-6}$. For $\tau=10^{-3}$ we use the
staged schedule $0.2,0.05,0.01,0.003,10^{-3}$; for $\tau=10^{-6}$ we append a
final $10^{-6}$ stage. Table~\ref{tab:soft-fqi-annealing-sensitivity} reports
median stationary projected Bellman error over 200 datasets. Annealing remains
a small effect at both temperatures: the largest median change is $1.35\%$ at
$\tau=10^{-3}$ and $1.21\%$ at $\tau=10^{-6}$.

\begin{table}[t]
\centering
\caption{Annealing sensitivity. Entries are median stationary projected
Bellman error over 200 offline datasets. Gain is
$(\mathrm{direct}-\mathrm{annealed})/\mathrm{direct}$.}
\label{tab:soft-fqi-annealing-sensitivity}
\begin{tabular}{lllccc}
\toprule
\(\tau\) & Regime & Method & Direct & Annealed & Gain \\
\midrule
\(10^{-3}\) & On-policy & Unweighted & 0.526 & 0.521 & 0.94\% \\
\(10^{-3}\) & On-policy & Oracle & 0.516 & 0.510 & 1.05\% \\
\(10^{-3}\) & On-policy & Estimated & 0.533 & 0.527 & 1.05\% \\
\(10^{-3}\) & Mild shift & Unweighted & 0.822 & 0.819 & 0.37\% \\
\(10^{-3}\) & Mild shift & Oracle & 0.511 & 0.506 & 1.04\% \\
\(10^{-3}\) & Mild shift & Estimated & 0.584 & 0.577 & 1.17\% \\
\(10^{-3}\) & Severe shift & Unweighted & 0.798 & 0.788 & 1.26\% \\
\(10^{-3}\) & Severe shift & Oracle & 0.595 & 0.591 & 0.77\% \\
\(10^{-3}\) & Severe shift & Estimated & 0.839 & 0.832 & 0.82\% \\
\(10^{-6}\) & On-policy & Unweighted & 0.529 & 0.524 & 0.94\% \\
\(10^{-6}\) & On-policy & Oracle & 0.519 & 0.515 & 0.80\% \\
\(10^{-6}\) & On-policy & Estimated & 0.533 & 0.529 & 0.79\% \\
\(10^{-6}\) & Mild shift & Unweighted & 0.811 & 0.808 & 0.38\% \\
\(10^{-6}\) & Mild shift & Oracle & 0.509 & 0.505 & 0.85\% \\
\(10^{-6}\) & Mild shift & Estimated & 0.581 & 0.574 & 1.09\% \\
\(10^{-6}\) & Severe shift & Unweighted & 0.798 & 0.789 & 1.21\% \\
\(10^{-6}\) & Severe shift & Oracle & 0.623 & 0.617 & 0.83\% \\
\(10^{-6}\) & Severe shift & Estimated & 0.849 & 0.845 & 0.42\% \\
\bottomrule
\end{tabular}
\end{table}
