\section{Additional Experimental Details}
\label{app:experiments}

\paragraph{Data-generating processes.}
The simulations are discounted MDPs with continuous states
\(S\in\mathbb{R}^d\), three discrete actions, nonlinear rewards, nonlinear
transitions, stochastic behavior policies, and shifted target policies. The
target-policy value is computed using independent Monte Carlo oracle rollouts.
Training transitions, cross-calibration folds, Bellman-evaluation transitions, initial
evaluation states, and oracle rollouts are generated from independent random
seeds.

\paragraph{Baseline value predictors.}
Each method first fits a \(Q\)-function from the offline behavior-policy data
and then forms
\[
  \widehat V(s)=\sum_a \pi(a\mid s)\widehat Q(s,a).
\]
The experiments use random-feature FQE and linear FQE because these families
expose two transparent error mechanisms: finite Bellman-iteration bias and
monotone or affine value-scale misspecification.

\paragraph{Strict cross-calibration.}
For fold \(k\), the \(Q\)-learner is fit on the other folds. The held-out fold
supplies \((\widehat V^{(-k)}(S_i),\widehat V^{(-k)}(S_i'),R_i)\). These
out-of-fold tuples are pooled to fit a single value-space calibration map by
importance-weighted fitted value iteration. At evaluation time, calibrated
values are aggregated as
\[
  \widehat V_{\mathrm{cal}}(s)
  =
  \mathrm{median}_{k=1,\ldots,K_{\mathrm{fold}}}
  g\!\left(\widehat V^{(-k)}(s)\right).
\]
The matched uncalibrated comparator is a \(Q\)-learner refit on all available
training data.

\paragraph{Value-space fitted value iteration.}
Let \(\rho_i=\pi(A_i\mid S_i)/\mu(A_i\mid S_i)\). In all reported runs the
action-ratio weights are clipped at 20 and normalized to mean one within each
calibration fit. Starting from the identity map, calibration iterates
\[
  g_{t+1}\in\arg\min_g\sum_i \rho_i
  \left[g(\widehat V(S_i))-\{R_i+\gamma g_t(\widehat V(S_i'))\}\right]^2.
\]
The implemented calibrators are weighted affine regression, weighted histogram
binning, weighted isotonic regression, and a weighted isotonic-histogram
hybrid.

\paragraph{Metrics.}
The scalar OPE estimate is the mean of \(g(\widehat V(S_0))\) over independent
initial evaluation states. The main function-level metric is held-out
value-function MSE,
\[
  \mathbb{E}\!\left[\{g(\widehat V(S))-V^\pi(S)\}^2\right],
\]
estimated using independent target-policy oracle values. Bellman calibration
error is estimated on 50,000 independent Bellman-evaluation transitions by binning
\(g(\widehat V(S))\) into 50 quantile bins, with a target minimum bin size of
1,000 observations, and averaging the weighted squared gaps between bin-mean
predictions and bin-mean Bellman outcomes
\[
  r_0(S,A)+\gamma g(\widehat V(S')) .
\]
Raw outputs also store a cross-fitted debiased calibration-error estimate based
on the moment
\(\mathbb{E}_w[(Y-\Delta)(\widehat\gamma(\Delta)-\Delta)]\), together with the
plug-in and floored debiased estimates, importance-weight effective sample
size, maximum weight, runtimes, and failure flags.

\subsection{Deep OPE/RL Unplugged \texttt{cheetah\_run}}
\label{app:cheetah-benchmark}

\paragraph{Policy-value calibration.}
We use the Deep OPE/RL Unplugged \texttt{cheetah\_run} policy snapshots as a
standard continuous-control benchmark for post-hoc value correction. The
benchmark bundle provides, for each target policy, an official FQE-L2 scalar
policy-value estimate and an official return estimate. We use three official
learning curves, each with eight policy snapshots in released order. Let
\(Z_{cj}\) denote the official FQE-L2 estimate for snapshot \(j\) on curve
\(c\), and let \(J_{cj}\) denote its official return. The raw score is
\(Z_{cj}\). Linear calibration fits \(a+bZ_{cj}\) by least squares on
calibration policies; isotonic calibration fits a monotone map from \(Z_{cj}\)
to \(J_{cj}\). Performance is the mean absolute OPE error
\(|g(Z_{cj})-J_{cj}|\) on held-out policies, reported relative to the raw
FQE-L2 error \(|Z_{cj}-J_{cj}|\).

Within each curve, we use three policy-disjoint splits: policies \(0\)--\(3\)
for calibration and \(4\)--\(7\) for evaluation, policies \(0,2,4,6\) for
calibration and \(1,3,5,7\) for evaluation, and policies \(0\)--\(4\) for
calibration and \(5\)--\(7\) for evaluation. This benchmark isolates the
value-scale component of the method on a standard OPE task: the base FQE-L2
scores are fixed before calibration, and the fitted one-dimensional map is
evaluated only on policies not used to fit that map.

\paragraph{Model-based FQE reproduction.}
For a model-based version, we load
\texttt{rlu\_control\_suite/cheetah\_run} through TFDS/RLDS and train a single
FQE critic for each target policy using the public Google Research
\texttt{policy\_eval} architecture: a two-hidden-layer \((256,256)\) critic on
state-action pairs, AdamW with learning rate \(3\cdot10^{-4}\), weight decay
\(10^{-5}\), target-network soft updates with \(\tau=0.005\), normalized states
and rewards, and clipped Bellman targets. We first compare the learned critic's
initial-state value estimate with the official FQE-L2 policy-value estimate.
Bellman calibration is then fit on held-out transitions by regressing
\(\widehat V(S)\) on \(R+\gamma \widehat V(S')\), and evaluated on separate
held-out episodes. Official returns are used only for scalar OPE evaluation, not
for fitting the critic or Bellman calibration map.

\paragraph{Reproducibility.}
The strict-cross submission run used 100 replications and the configuration
\path{configs/strict_cross_submission_suite.yaml} in the
\path{FQE_calibration_neurips} experiment directory. Raw replication-level
results, grouped summaries, validation output, and the figure-generation script
are stored with the same directory under
\path{results/paper_strict_cross_submission_v3_50k}.
